### 2021-07-30 paper/localpsf.tex
starting on boundary extension discussion

\subsection{Computation, evaluation, and storage of impulse responses}
\label{sec:get_impulse_response}

@@

\subsection{Boundary impulse response extension}
\label{sec:boundary_extension}

@@

The basic ideas behind H-matrices are as follows:
\begin{itemize} 
	\item Often, large dense matrices of practical interest may be permuted, then partitioned into blocks recursively, in such a way that many off-diagonal blocks of the matrix are numerically low rank, even if the matrix is high rank.
	\item Recursive algorithms can take advantage of this low rank block structure to perform matrix arithmetic fast. Conventional algorithms for matrix inversion, matrix factorization, matrix-vector products, matrix-matrix products, and matrix addition require either $O(N^2)$ or $O(N^3)$ time and memory, while the aforementioned recursive algorithms can perform these matrix operations in $O(N \log^a N)$ time and memory for H-matrices. Here $a=0, 1, 2$, or $3$ depending on the operation and type of H-matrix.
\end{itemize}
For more details on H-matrices, we recommend \cite{HMATRIXGOOD}.

The H-matrix construction process that we use to form the matrix $\AkerPcMat$ proceeds as follows. First, we construct hierarchical partitionings of the degrees of freedom for the columns and rows of the matrix (cluster trees, Section \ref{sec:cluster_trees}). Second, we construct a hierarchical partitioning of the blocks of the matrix, in such a way that many of the blocks in the partitioning are expected to be low rank, and the remaining high rank blocks are small (block cluster tree, Section \ref{sec:block_cluster_tree}). Finally, we form low rank approximations of the blocks of the matrix that are expected to be low rank (adaptive cross approximation, Section \ref{sec:adaptive_cross}), and fill in the remaining high rank  blocks with their numerical values. The first two steps require geometric information about the spatial locations of the degrees of freedom associated with the rows and columns of the matrix, but these steps do not depend on the particular values of matrix entries. The third step requires us to evaluate $O(N \log N)$ specially-chosen entries of $\widetilde{A}$, and we evaluate these entries using the method described in Section \ref{sec:eval_matrix_entries}.

\subsection{Cluster trees}
\label{sec:cluster_trees}

@@

\subsection{Block cluster tree} 
\label{sec:block_cluster_tree}

@@

\subsection{Adaptive cross low rank approximation of blocks}
\label{sec:adaptive_cross}

>>>>

\subsection{Computation and storage of convolution kernels}
\label{sec:get_impulse_response}

@@

\subsection{Addressing convolution kernel boundary artifacts}
\label{sec:boundary_extension}

Evaluating the kernel for our product-convolution approximation requires evaluating $\varphi_{x_i}(y-x)$. But this may be undefined, because $y-x$ may reside outside the support of $\varphi_{x_i}$, even if $x \in \Omega$ and $y \in \Omega$. The default approach to deal with this problem is to extend $\varphi_{x_i}$ by zero wherever it is undefined. But this leads to substantial errors, known as boundary artifacts, when the sample point $x_i$ is near the boundary of the domain. In this case, the impulse response is artificially chopped off by the domain boundary. See Figure FIG for an illustration, and see \cite{ADAPTIVECONVMYPAPER} for a more detailed discussion of boundary artifacts in.

To address boundary artifacts, we fill in missing/undefined portions of convolution kernels using values from convolution kernels for nearby sample points. This is similar to the approach used in \cite{ADAPTIVECONVMYPAPER}, except

@@

Often, large dense matrices of practical interest may be permuted, then partitioned into blocks recursively, in such a way that many off-diagonal blocks of the matrix are numerically low rank, even if the matrix is high rank. Such matrices are known as hierarchical matrices (H-matrices). Many classes of H-matrices exist (H1, H2, HSS, HBS, and more), and all of these types of H-matrices could be used in conjunction with our product-convolution approximation. Here we use classical H1 matrices. For this section, when we say H-matrix, we are referring to H1 matrices.

While a dense $N \times N$ matrix traditionally requires $O(N^2)$ memory to store, H-matrices may be stored using $O(N \log N)$ memory, by storing only the low rank factors for the low rank blocks. Recursive algorithms can take advantage of the H-matrix low rank block structure to perform matrix arithmetic fast. Conventional dense matrix algorithms for matrix inversion, matrix factorization, matrix-vector products, matrix-matrix products, and matrix-matrix addition require either $O(N^2)$ or $O(N^3)$ time and memory, while the aforementioned recursive algorithms can perform these matrix operations in $O(N \log^a N)$ time and memory for H-matrices. Here $a=0, 1, 2$, or $3$ depending on the operation and type of H-matrix. For more details on H-matrices, we recommend \cite{HMATRIXGOOD}.

\subsection{H-matrix construction}

The H-matrix construction process that we use to form the H-matrix representation of $\AkerPcMat$ proceeds as follows. First, we construct hierarchical partitionings of the degrees of freedom for the columns and rows of the matrix (cluster trees, Section \ref{sec:cluster_trees}). Second, we construct a hierarchical partitioning of the blocks of the matrix, in such a way that many of the blocks in the partitioning are expected to be low rank, and the remaining high rank blocks are small (block cluster tree, Section \ref{sec:block_cluster_tree}). Finally, we form low rank approximations of the blocks of the matrix that are expected to be low rank (adaptive cross approximation, Section \ref{sec:adaptive_cross}), and fill in the remaining high rank  blocks with their numerical values. The first two steps require geometric information about the spatial locations of the degrees of freedom associated with the rows and columns of the matrix, but these steps do not depend on the particular values of matrix entries. The third step requires us to evaluate $O(N \log N)$ specially-chosen entries of $\AkerPcMat$, and we evaluate these entries using \eqref{eq:Akerpcmat_entries}.

\subsubsection{Cluster trees}
\label{sec:cluster_trees}

@@

\subsubsection{Block cluster tree} 
\label{sec:block_cluster_tree}

@@

\subsubsection{Adaptive cross low rank approximation of blocks}
\label{sec:adaptive_cross}
